### 2021-07-09 doc/thesis/chapters/implementation.tex
write stuff
text update
add some thoughts

%%%%%%%%%%%%%%%%%%%%
\chapter{Implementation}
\label{cha:Implementation}
\section{Matlab/Python Model}
  in fixed point, close to hardware level algorithm

@@

>>>>

%%%%%%%%%%%%%%%%%%%%
\chapter{Implementation}
\label{cha:Implementation}

\section{Detailed block diagram of digital signal processing chain}

\includepicture [1.0] [0] {Detailed block diagram of the digital signal processing chain.} {bd_dsp_detailed} {img/bd_detailed_dsp}

\section{Matlab Model}

in fixed point, close to hardware level algorithm

\subsection{Transmitter block diagram}

\section{GNU Radio}
  \subsection{Introduction}
  \subsection{Transmitter}
  \subsection{Receiver}

@@

  TODO: \\
  - comparison of VHDL vs HLS\\
  - in the point of view:\\
  - system integration (IP generation, AXI interfaces),\\
  - logic utilization\\
--> see introduction.tex

### 2021-07-09 doc/thesis/chapters/system-architecture-and-concept.tex
add some thoughts

The aim of this thesis is develop a system architecture and concept, that allows the implementation of an FM radio receiver in multiple different ways, while providing an elegant way to compare the different solutions.
The final goal thereby is always be the same, that is: Listen to the music of a radio station that is transmitted over FM broadcast radio.

@@

As already mentioned above, multiple ways of technology and implementation can lead to a similar result.
Thus, the next step is to define a set of possible ways, which will actually be implemented.
For this thesis, the decision was made to implement the FM radio receiver, using the following methods.

@@

In order to implement an FM radio receiver, all of the listed methods require deep knowledge about the neccessary details of signal processing.
However, the implementation of the various different methods require more or less knowledge and effort on the exact underlying implementation of each signal processing part.
This depends on their level of abstraction.

>>>>

The aim of this thesis is develop a system architecture and concept, that allows the implementation of an FM radio receiver in multiple different ways, while providing an elegant way to compare the different solutions.
The final goal thereby is always be the same, that is: Listen to the music of a radio station that is transmitted over FM broadcast radio.\\

@@

As already mentioned above, multiple ways of technology and implementation can lead to a similar result.
Thus, the next step is to define a set of possible ways which will actually be implemented.
For this thesis, the decision was made to implement the FM radio receiver by using the following methods.

@@

In order to implement an FM radio receiver, all of the listed methods require deep knowledge about the neccessary details of signal processing.
However, the implementation of the various different methods require more or less knowledge and effort on the exact underlying implementation of each signal processing part.
This depends on their respective level of abstraction.
